\myTitle

### 2023-12-13 body-text-of-paper.tex
Some small additions

A best practice for evaluating the behavior of genetic clustering algorithms on an empirical dataset is to conduct
parallel analyses on simulated data where the truth is known, yet structured to mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine}.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see CITE, CITE, CITE).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals back to source populations.
We refer to this phenomenon as resampling-induced power inflation (RIPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

@@

In response to these needs, we developed \gscramble{} – a simulation approach that samples alleles from respective populations without
replacement, thus maintaining the genetic differences in the empirical dataset and eliminating the effect of RIPI.
Further, by simulating individual genotypes based on user-defined pedigrees, \gscramble{} allows for the simulation of admixed genotypes of
varying degrees of complexity while allowing the tracking of haplotype blocks from source populations within the specified pedigree.
By integrating species-specific recombination rates, \gscramble{} simulates biologically informed genotypes that mirror empirical data.
We develop and illustrate \gscramble{} with use of single nucleotide polymorphic (SNP) genotypes.

@@

Before we proceed to a description of the methodology used by \gscramble{},
we demonstrate a case in which using a standard sampling-with-replacement
approach induces RIPI when estimating admixture fractions.
To construct this simple example, we used the R programming language \citep{Rcoreteam} to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$, each of size $N$ diploid genotypes. The genotypes in $A$ and $B$ were simulated
from the same allele frequencies assuming Hardy-Weinberg equilibrium.

@@

Because the simulations were done in a na\"{i}ve way that effectively assumes that the population
allele frequencies are identical to those observed in the samples themselves, we hypothesized that ADMIXTURE would return estimates of
$q_A$ that were
centered around the true values, even though samples $A$ and $B$ were drawn from the same
population.
We further expected that ADMIXTURE would return more accurate estimates of
$q_A$ when $N$ was smaller and the number of loci was larger.
We summarized the results by plotting boxplots of the ADMIXTURE-inferred $q_A$ values,
 for the 480 newly simulated individuals (and for the original samples, $A$ and $B$, in the
 case of unsupervised clustering),
for each combination of $L$, $N$, and $n$.

@@

We refer to the structure used to implement this cross-validation simulation
of admixed individuals
a {\em genomic simulation pedigree} or GSP.  Like any pedigree,
a GSP includes a set of founders (individuals that have no parents specified in the
pedigree), and it includes non-founders; however, we introduce an additional node
type in the GSP that represents samples taken from the non-founders. These samples
are the simulated admixed individuals.  A GSP must have no inbreeding loops, since
any inbreeding loop indicates that more than one copy of a gene in an ancestor may
be created amongst its descendants, which is a type of sampling without
replacement.  Furthermore, in a GSP, the amount of genetic material taken from the
samples at the sample nodes should be equal to the amount of material in the founders,
to ensure that all available data is being used to estimate power for the estimation of
admixture fractions.

Figure~\ref{fig:gsp1} shows an example GSP for the simple case
of simulating $F_2$ individuals. The figure and its caption
should be studied, as the following section
uses terminology that is defined in the figure caption.
%%%%%%%%%%%
\begin{figure}
\newcommand{\gspcapone}{\footnotesize
A genomic simulation pedigree (GSP) for simulating $F_2$ individuals.
Squares denote founder and non-founder nodes in the pedigree. There are four founders in the pedigree,
individuals 1--4.  The inverted triangles above each of those founders denotes, in color
and text, the population of origin of each of the two genomes within each founder.
Thus, individuals~1 and~2 are founders purely from population~$A$, and~3 and~4
are purely from population~$B$.  The pink hexagon labeled s7 is the sample node.
It represents samples that are taken from non-founder node~7, which, from the structure
of the pedigree, clearly represents an $F_2$ hybrid between populations $A$ and $B$.  The red numbers
on edges above and leading into each non-founder node indicate the number of
gametes that get segregated from the parent node (at the top of the edge) to the
daughter node (at the bottom of the edge).
This emphasizes that,
in dropping genes through a GSP, in contrast
to a traditional pedigree, each parent
node may segregate multiple gametes to a daughter node.  See the text for
further explanation.
Each non-founder node $x$ will have exactly two edges coming into it from above
(from its two parents), we denote the numbers associated with those edges as $G^+_{x,1}$ and $G^+_{x,2}$.
For example, node 6 has $G^+_{6,1}=G^+_{6,2} = 2$.
A non-founder individual may have more or less than two edges coming downward
out of it.  Letting $e_x$ be the number of downward edges out of node $x$ to its $e_x$
non-founder daughter nodes, we denote the number of gametes segregated
through each edge as $G^{-}_{x, 1},\ldots,G^{-}_{x, e_x}$.  For example,
non-founder node~5, $e_5 = 1$ and $G^{-}_{5,1}=4$.
Finally, the purple number adjacent to the edge leading into the
sample node indicates how many sample individuals are drawn from individual
node 7. Any non-founder individual node can have a maximum of one edge leading
to a sample node.  We denote the number of samples emanating from node $x$
node as $S_x$. In our example $S_7=4$ indicates that four $F_2$ individuals are
created from a single simulation on this GSP.
}
\begin{center}
\includegraphics[width=\columnwidth]{figures/F2.pdf}
\end{center}
\caption[\gspcapone]{\gspcapone}
\label{fig:gsp1}
\end{figure}
%%%%%%%%%%%%
It is important to understand that, apart from the founder nodes, the individual
nodes in a GSP do not necessarily represent only a single individual.  Specifically,
since we are preserving all genetic material, multiple gametes may get segregated
through each non-founder node in a GSP\@.

Genetic material is segregated through
a GSP using these steps, done upon each node in an order such that the steps
are run on each node's parents before being run on the node itself:
\begin{enumerate}
\item Each genome in a triangle above a founder node represents a gamete
carrying a single, haploid copy of the genome.
These gametes are united within the founder individual and then
following recombination between each chromosome
with probability $\frac{1}{2}$ and within each chromosome according to
a user-specified recombination map,
 one gamete is assorted down each edge from the founder node to its daughter.
\item Each non-founder node, $x$, will have exactly two edges coming
into it---one from each parent.  Each of the $G^+_{x,1}$ gametes coming in from the
first edge is united with a single one of the $G^+_{x,2}$ gametes coming
in on the second edge (in a random order).
\item If a non-founder node $x$ has an edge to a sample node,
a randomly chosen $S_x$ of the united pairs of gametes are delivered
to the sample node to constitute the $S_x$ samples taken from individual
node $x$. Any remaining united pairs of gametes are treated as in (4) below.
\item United pairs of gametes (including those remaining after delivery
to a sample node) in each non-founder node $x$ are segregated into
gametes with recombination, and each of these gametes is assigned, in
random order, to the gamete edges proceeding downward out of the node,
with the number of gametes assigned to the $i\thh$ downward edge being
$G^-_{x,i}$.
\end{enumerate}
At the end of this process, the samples simulated (as united pairs of gametes)
into the sample nodes will contain all of the genetic material (and no more) found among the founders but that
material will have been segregated and recombined according to the pedigree.  Thus the
samples obtained from a GSP can be simulated with the expected admixture fractions
for any hybrid category that can be specified by a pedigree.  They have also been simulated
in a way that 1) reflects physical linkage---each individual inherits segments of the genome
simulated using a recombination map; 2) does not duplicate any genetic material---the sampling of
genetic material is entirely without replacement so it will not induce RIPI; and 3) no genetic material has been lost---all the genetic material of the founders
is represented in the samples, maximizing the number of individuals and markers available to
use in downstream analyses.

@@

\gscramble{} uses a GSP to segregate segments of genetic material from the founders
to the samples.  At the end of segment simulation, the genome of each sample
is recorded as a mosaic of segments that derive from different founders.  In order
to create a data set of markers in each sample, it is necessary only to identify the alleles
that occurred on each segment within the founders and propagate those alleles to the
corresponding segments within the samples.  At the stage of assigning alleles to
founders, \gscramble{} provides a variety of ways to permute alleles amongst
the collection of individuals from which the founders are drawn.  By using permutation,
variability in the data is created, but, since it is done without sampling with replacement, it does
not induce RIPI.

@@

Permutation of alleles is handled within the \gscramble{} function {\footnotesize\tt segments2markers()}
which takes as input the segments segregated down a GSP, a matrix of sampled genotypes, and a specification
of the group that each sampled individual belongs to.  The permutation performed when running
{\footnotesize\tt segments2markers()} is controlled by two main options.  The first, {\tt\footnotesize preserve\_individuals},
can take three different values.  If {\tt\footnotesize preserve\_individuals = TRUE}, then entire individuals are permuted,
such that all the alleles within an individual remain together.  If {\tt\footnotesize preserve\_individuals = "BY\_CHROM"}, then
the alleles within an individual found on a homologous pair of chromosomes remain together, but the different
chromosome pairs of an individual are independently permuted into new positions in the data set.  This form of permutation
maintains the linkage disequilibrium (LDL between markers on the same chromosome, which may be desirable in some contexts.
If {\tt\footnotesize preserve\_individuals = FALSE} then each gene copy within an individual is permuted separately,
providing the maximal scrambling of the data. The second option, {\tt\footnotesize preserve\_haplotypes}, can take two
different values, {{\tt\footnotesize FALSE} (the default) and {\tt\footnotesize TRUE}.
This option, which keeps alleles together
on the same haplotype, should be set to true only
if the original genotypes are phased into separate haplotypes.

%%%%%%%
\newcommand{\permcap}{\footnotesize An illustration of how \gscramble{} permutes data under
different options.  {\bf (a)}~A picture
representing an original data set of $N=12$ diploids sampled from three populations and typed at $L=15$ markers.
Different colors represent different sampled individuals. Individuals 1--5 are shades of blue and green, indicating that they
are from a single population.  Individuals 6--9 are from another population, (shades of red and orange), while 10--12
are from a third population and are colored shades of violet. Thick vertical black lines separate the different
populations.  Markers are shown in rows. There are 6 markers on the first chromosome, 5 on the second, and 4 on the
third.  Each chromosome is delimited by a thick, horizontal black line. The "a" and the "b" in the colored cells denote the first and second gene copies within an individual at each marker.  It is worth noting that this representation shows a $2L \times N$ matrix,
which is the transpose of the $N\times 2L$ matrix used to supply genetic marker data to \gscramble{}. {\bf (b)}~Examples of how the {\tt\footnotesize preserve\_individuals} and {\tt\footnotesize preserve\_haplotypes} options of the {\tt\footnotesize segments2markers()}
function affect the permutation of
the genetic data of the original data set.  Panel headers show the option values while the colors and "a" and "b" values
in the colored cells show the original position of each gene copy in the original sample.  Note that permutation is always
done within the populations.  When {\tt\footnotesize preserve\_individuals = TRUE},  then just the
individuals in their entirety are permuted.  When {\tt\footnotesize preserve\_individuals = "BY\_CHROM"}, each pair
of a single chromosome within an individual remains together when permuted. When {\tt\footnotesize preserve\_individuals = FALSE}, gene copies are freely permuted between individuals.  The option {\tt\footnotesize preserve\_haplotypes = TRUE} causes each haplotype on a chromosome to be preserved
while permuting. This option should only be used when the original data set is phased.
}
\begin{figure*}
\includegraphics[width=\textwidth]{figures/permutations-plot.png}
\caption[\permcap]{\permcap}
\end{figure*}
%%%%%%%

@@

>>>>

A best practice for evaluating the behavior of genetic clustering algorithms on an empirical dataset is to conduct
parallel analyses on simulated data where the truth is known, yet structured to mirror the empirical data set
as closely as possible \citep{vaha2006efficiency,anderson2008improved,latch2011fine}.
Techniques to simulate individual genotypes in this context frequently use sampling with replacement from the
observed allele frequencies (see CITE, CITE, CITE).
However, sampling with replacement implicitly increases the pairwise genetic distance among simulated samples, relative to the observed
samples, and
inflates the perceived statistical power to correctly assign individuals back to source populations.
We refer to this phenomenon as resampling-induced, spurious power inflation (RISPI).
\citet{anderson2008improved} used simulations to document this type of artifact in the context of
genetic stock identification (GSI), a type of clustering application in which individuals are constrained to have
all their ancestry from a single subpopulation.
Similar statistical artifacts occur when simulating data to
assess how accurately admixture fractions can be estimated.

@@

In response to these needs, we developed \gscramble{} – a simulation approach that samples alleles from respective populations without
replacement, thus maintaining the genetic differences in the empirical dataset and eliminating the effect of RISPI.
Further, by simulating individual genotypes based on user-defined pedigrees, \gscramble{} allows for the simulation of admixed genotypes of
varying degrees of complexity while allowing the tracking of haplotype blocks from source populations within the specified pedigree.
By integrating species-specific recombination rates, \gscramble{} simulates biologically informed genotypes that mirror empirical data.
We develop and illustrate \gscramble{} with use of single nucleotide polymorphic (SNP) genotypes.

@@

Before we proceed to a description of the methodology used by \gscramble{},
we demonstrate a case in which using a standard sampling-with-replacement
approach induces RISPI when estimating admixture fractions.
To construct this simple example, we used the R programming language \citep{Rcoreteam} to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$, each of size $N$ diploid genotypes. The genotypes in $A$ and $B$ were simulated
from the same allele frequencies assuming Hardy-Weinberg equilibrium.

@@

Because the simulations were done in a na\"{i}ve way that effectively assumes that the population
allele frequencies are identical to those observed in the samples themselves, we hypothesized that ADMIXTURE would return estimates of
$q_A$ that were
centered around the simulated values, even though samples $A$ and $B$ were drawn from the same
population. In other words, we expected to observe RISPI.
We further expected that ADMIXTURE would return more accurate estimates of the simulated
$q_A$ values when $N$ was smaller and the number of loci was larger.
We summarized the results by plotting boxplots of the ADMIXTURE-inferred $q_A$ values,
 for the 480 newly simulated individuals (and for the original samples, $A$ and $B$, in the
 case of unsupervised clustering),
for each combination of $L$, $N$, and $n$.

@@

We refer to the structure used to implement this cross-validation simulation
of admixed individuals as
a {\em genomic simulation pedigree} or GSP.  Like any pedigree,
a GSP includes a set of founders (individuals that have no parents specified in the
pedigree), and it includes non-founders; however, we introduce an additional node
type in the GSP that represents samples taken from the non-founders. These samples
are the simulated admixed individuals.  A GSP must have no inbreeding loops, since
any inbreeding loop indicates that more than one copy of a gene in an ancestor may
be created amongst its descendants, which is a type of sampling without
replacement.  Furthermore, in a GSP, the amount of genetic material taken from the
samples at the sample nodes should be equal to the amount of material in the founders,
to ensure that all available data is being used to estimate power for the estimation of
admixture fractions.

Figure~\ref{fig:gsp1} shows an example GSP for the simple case
of simulating $F_2$ individuals. The figure and its caption
should be studied, as the following section
uses terminology that is defined in the figure caption.
%%%%%%%%%%%
\begin{figure}
\newcommand{\gspcapone}{\footnotesize
A genomic simulation pedigree (GSP) for simulating $F_2$ individuals.
Squares denote founder and non-founder nodes in the pedigree. There are four founders in the pedigree,
individuals 1--4.  The  triangles above each of those founders denotes, in color
and text, the population of origin of each of the two genomes within each founder.
Thus, individuals~1 and~2 are founders purely from population~$A$, and~3 and~4
are purely from population~$B$.  The pink hexagon labeled s7 is the sample node.
It represents samples that are taken from non-founder node~7, which, from the structure
of the pedigree, clearly represents an $F_2$ hybrid between populations $A$ and $B$.  The red numbers
on edges above and leading into each non-founder node indicate the number of
gametes that get segregated from the parent node (at the top of the edge) to the
daughter node (at the bottom of the edge).
This emphasizes that,
in dropping genes through a GSP, in contrast
to a traditional pedigree, each parent
node may segregate multiple gametes to a daughter node.  See the text for
further explanation.
Each non-founder node $x$ will have exactly two edges coming into it from above
(from its two parents), and we denote the numbers associated with those edges as $G^+_{x,1}$ and $G^+_{x,2}$.
For example, node 6 has $G^+_{6,1}=G^+_{6,2} = 2$.
A founder individual may have, at most, 2 edges coming downward out of it, while a non-founder individual may have more or less than two edges coming downward
out of it.  Letting $e_x$ be the number of downward edges out of node $x$ to its $e_x$
non-founder daughter nodes, we denote the number of gametes segregated
through each edge as $G^{-}_{x, 1},\ldots,G^{-}_{x, e_x}$.  For example, at
non-founder node~5, $e_5 = 1$ and $G^{-}_{5,1}=4$.
Finally, the purple number adjacent to the edge leading into the
sample node indicates how many sample individuals are drawn from individual
node 7. Any non-founder individual node can have a maximum of one edge leading
to a sample node.  We denote the number of samples emanating from node $x$ as $S_x$. In our example $S_7=4$ indicates that four $F_2$ individuals are
created from a single simulation on this GSP.
}
\begin{center}
\includegraphics[width=\columnwidth]{figures/F2.pdf}
\end{center}
\caption[\gspcapone]{\gspcapone}
\label{fig:gsp1}
\end{figure}
%%%%%%%%%%%%
It is important to understand that, apart from the founder nodes, the individual
nodes in a GSP do not necessarily represent only a single individual.  Specifically,
since we are preserving all genetic material, multiple gametes may get segregated
through each non-founder node in a GSP\@.

Genetic material is segregated through
a GSP using these steps, done upon each node in an order such that the steps
are run on each node's parents before being run on the node itself:
\begin{enumerate}
\item Each genome in a triangle above a founder node represents a gamete
carrying a single, haploid copy of the genome.
These gametes are united within the founder individual and then
recombination occurs between each chromosome
with probability $\frac{1}{2}$ and within each chromosome according to
a user-specified recombination map to create two new gametes, which are
recombined version of the original ones.  These two gametes are then segregated at random down the edge (or edges) from the founder node. Upon each edge, $i$ from founder node $f$, $G^-_{f,i}$ gametes are segregated. 
\item Each non-founder node, $x$, will have exactly two edges coming
into it---one from each parent.  Each of the $G^+_{x,1}$ gametes coming in from the
first edge is united with a single one of the $G^+_{x,2}$ gametes coming
in on the second edge (in a random order).
\item If a non-founder node $x$ has an edge to a sample node,
a randomly chosen $S_x$ of the united pairs of gametes are delivered
to the sample node to constitute the $S_x$ samples taken from individual
node $x$. Any remaining united pairs of gametes are treated as in (4) below.
\item United pairs of gametes (including those remaining after delivery
to a sample node) in each non-founder node $x$ are segregated into
gametes with recombination, and each of these gametes is assigned, in
random order, to the gamete edges proceeding downward out of the node,
with the number of gametes assigned to the $i\thh$ downward edge being
$G^-_{x,i}$.
\end{enumerate}
At the end of this process, the samples simulated (as united pairs of gametes)
into the sample nodes will contain all of the genetic material (and no more) found among the founders, but that
material will have been segregated and recombined according to the pedigree.  Thus the
samples obtained from a GSP can be simulated with the expected admixture fractions
for any hybrid category that can be specified by a pedigree.  They have also been simulated
in a way that 1) reflects physical linkage---each individual inherits segments of the genome
simulated using a recombination map; 2) does not duplicate any genetic material---the sampling of
genetic material is entirely without replacement so it will not induce RISPI; and 3) no genetic material has been lost---all the genetic material of the founders
is represented in the samples, maximizing the number of simulated individuals and markers available to
use in downstream analyses.

@@

\gscramble{} uses a GSP to segregate segments of genetic material from the founders
to the samples.  At the end of segment simulation, the genome of each sample
is recorded as a mosaic of segments that derive from different founders.  In order
to create a data set of markers in each sample, it is necessary only to identify the alleles
that occurred on each segment within the founders and propagate those alleles to the
corresponding segments within the samples.  At the stage of assigning alleles to
founders, \gscramble{} provides a variety of ways to permute alleles amongst
the collection of individuals from which the founders are drawn.  By using permutation,
variability in the data is created, but, since it is done without sampling with replacement, it does
not induce RISPI.

@@

Permutation of alleles is handled within the \gscramble{} function {\footnotesize\tt segments2markers()}
which takes as input the segments segregated down a GSP, a matrix of sampled genotypes, and a specification
of the group that each sampled individual belongs to.  The permutation performed when running
{\footnotesize\tt segments2markers()} is controlled by two main options.  The first, {\tt\footnotesize preserve\_individuals},
can take three different values.  If {\tt\footnotesize preserve\_individuals = TRUE}, then entire individuals are the unit that gets permuted within the
data set,
such that all the alleles within an individual remain together.  If {\tt\footnotesize preserve\_individuals = "BY\_CHROM"}, then
the alleles within an individual found on a homologous pair of chromosomes remain together, but the different
chromosome pairs of an individual are independently permuted into new positions in the data set.  This form of permutation
maintains the linkage disequilibrium (LD) between markers on the same chromosome, which may be desirable in some contexts.
If {\tt\footnotesize preserve\_individuals = FALSE} then each gene copy within an individual is permuted separately,
providing the maximal scrambling of the data. The second option, {\tt\footnotesize preserve\_haplotypes}, can take two
different values, {{\tt\footnotesize FALSE} (the default) and {\tt\footnotesize TRUE}.
This option, which keeps alleles together
on the same haplotype, should be set to {\tt TRUE} only
if the original genotypes have been phased into separate haplotypes.
Fig.~\ref{fig:perms} depicts, graphically, the effect of using different settings of
{\tt\footnotesize preserve\_individuals} and 
{\tt\footnotesize preserve\_haplotypes}, together.

%%%%%%%
\newcommand{\permcap}{\footnotesize An illustration of how \gscramble{} permutes data under
different options.  {\bf (a)}~A picture
representing an original data set of $N=12$ diploids sampled from three populations and typed at $L=15$ markers.
Different colors represent different sampled individuals. Individuals 1--5 are shades of blue and green, indicating that they
are from a single population.  Individuals 6--9 are from another population, (shades of red and orange), while 10--12
are from a third population and are colored shades of violet. Thick vertical black lines separate the different
populations.  Markers are shown in rows. There are 6 markers on the first chromosome, 5 on the second, and 4 on the
third.  Each chromosome is delimited by a thick, horizontal black line. The "a" and the "b" in the colored cells denote the first and second gene copies within an individual at each marker.  It is worth noting that this representation shows a $2L \times N$ matrix,
which is the transpose of the $N\times 2L$ matrix used to supply genetic marker data to \gscramble{}. {\bf (b)}~Examples of how the {\tt\footnotesize preserve\_individuals} and {\tt\footnotesize preserve\_haplotypes} options of the {\tt\footnotesize segments2markers()}
function affect the permutation of
the genetic data of the original data set.  Panel headers show the option values while the colors and "a" and "b" values
in the colored cells show the original position of each gene copy in the original sample.  Note that permutation is always
done within the populations.  When {\tt\footnotesize preserve\_individuals = TRUE},  then just the
individuals in their entirety are permuted.  When {\tt\footnotesize preserve\_individuals = "BY\_CHROM"}, each pair
of a single chromosome within an individual remains together when permuted. When {\tt\footnotesize preserve\_individuals = FALSE}, gene copies are freely permuted between individuals.  The option {\tt\footnotesize preserve\_haplotypes = TRUE} causes each haplotype on a chromosome to be preserved
while permuting. This option should only be used when the original data set is phased.
}
\begin{figure*}
\includegraphics[width=\textwidth]{figures/permutations-plot.png}
\caption[\permcap]{\permcap}
\label{fig:perms}
\end{figure*}
%%%%%%%

@@

We illustrate the use of \gscramble{} in two examples.  The first involves
simulating a small number ($<\,$70) of markers that are fixed, or nearly
fixed, for alternate alleles between two species of trout: rainbow trout ({\em 
Oncorhynchus mykiss}) and cutthroat trout ({\em O. clarkii}). The goal of the 
simulation study is to determine how accurately individuals of different hybrid
categories between the species can be identified, and whether the use of linked 
markers deflates the estimates of uncertainty to an unacceptable degree.  The 
second example involves many more markers ($\approx$14,000) and 
investigates the accuracy for
identifying individuals admixed between closely related groups of feral
pigs in Missouri.
